Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-26 lloveras_2020.tex
mas texto y algunas imagenes

@@

\temp{
Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}. These non-reconstructed voxels are indicated as black voxels in the Carrington maps of the reconstructed DEMT reults in Section \ref{resu}.
}

@@

\albert{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, i.e.
$E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transversal area of the magnetic flux tube at position $s$. Under a quiescent solar corona plasma regime, the conductive flux is assumed to be dominated by the electron thermal conduction, described by the usual Spitzer model \citep{spitzer_1962}
\begin{equation}\label{Fc}
F_c(s)=-\kappa_0\,{T(s)}^{5/2}\,\frac{dT}{ds}(s),
\end{equation}
where $\kappa_0 = 9.2 \times 10^{-7}  {\rm erg\,sec^{-1}\,K^{-7/2}}$ is the Spitzer thermal conductivity.}

@@

\albert{The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube. Dividing the result by the flux tube ara at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + \phi_c.
\end{equation}
\noindent
where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},}\\
\notebyalbert{Diego, please include here Equations (11) and (12) of that paper, which incredibly enough will have the same numbers here.}

\albert{Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations (\ref{Fc})-(\ref{Er}). Once computed, the quantity $\phi_h$ can be calculated, which is the enery input flux required at the coronal base of each coronal field-line required to mantain a stable coronal structure.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{\albert{\emph{Top panels:} latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey) and closed (black) traced field lines for which there are along at least five DEMT data points, for both CR2082 (left) and CR2208 (right). \emph{Bottom panels}, latitude-longitude location (at the same height) of each traced leg that meets the criteria listed in Section \ref{trace}. Type 0, I, II and III legs (see text) are shown in blue, red, violet and green, respectively, for CR-2082 (left) and CR-2208 (right).}}
\label{rpoint_demt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{{Statistical distribution of DEMT results traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$. Results for target rotations CR2082 and CR2208 are shown in blue and red color, respectively. In each panel the median value $m$ is indicated.} \notebyalbert{ (by Albert) The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading. Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.} \albert{Also, I believe you should use a FIXED x-range for each quantity (one for $\NCB$, one for $\lambda_N$ and one for $\aTm$) accross all Figures 5, 12, and 13, as that will visually highlinght how meadians and standard deviations compare, both between targets (CR2082 versus CR2208, this Figure) as well as between models (DEMT versus AWSoM, Figures 12 and 13).}}
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
\caption{\albert{Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right). From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.} \notebyalbert{(by Albert) En el XYOUTS podés poner la letra griega $\phi$ usando los comandos ``!4" y ``!3",  y para que te salga r,c,h como subíndice pero no tan pequeño usá: ``!Dp!N", dónde p=r,c,h.}}
\label{energia_demt}
\end{center}
\end{figure}

\albert{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities $\phi_h$, $\phi_r$ and $\phi_c$ in green, blue and red color, respectively.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).} \notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the abslute minimum indicates the location of the HCS at this height. I believe it is interesting to compare these two curves with Figure 10. Note that while in this Figure all latitudes are magnetically open, in Figure 10 only the part at latitudes larger than the vertical black lines are open. Note that DEMT shows that in the open low corona $N_e$ dereases from the O/C boundary towards the poles, anti-correlating with the AWSoM terminal speed, which is nice. In order to quantify this anti-correlation we need to trace the termnal speed and the DEMT $N_e$, which we may need to do with the help of Chip and Nishtha. Chip, we can discuss this idea over Skype after Xmas if you are around.}}
\label{perf_lon_vr}
\end{center}
\end{figure}

@@

\diego{We could say something about the anti correlation between speed and density and not get into the trace because issues do always appear and we don't have much time, and we all want to be happy in january. Unless the collaborators find easy to make this part.}

>>>>

To perform the comparison two specific rotations were selected, CR-2082 (2009, 05 April through 03 May), a deep minimum period between solar cycles (SCs) 23 and 24 characterized by virtually no ARs, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24.

To determine the thermodynamical structure of both rotations, the DEMT technique was applied to respective time series of EUV images covering each first half rotation. To study CR-2082 and CR-2208 data taken by the EUVI/STEREO and AIA/SDO instruments was used, respectively.

In DEMT, the low corona in the height range $1.0$ to $1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic cell (or voxel) is set to 0.01 \rsun \ in the radial direction, while is set 2\deg\ in both the latitudinal and longitudinal directions. We carried out a reconstruction using half of a solar rotation blocking the lines-of-sight comming from the disk (i.e. only using off-limb data). With this angular resolution one image every 6 hours is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation. We refer the reader to \citet{frazin_2009} for a detailed description of the technique, and to \citet{vasquez_2016} for a recent review on all published work based on it. Here we summarize the key points. The technique involves two consecutive procedures.

 \diego{creo que es la primera vez que exploramos con hollow, vale la pena explicar la diferencia en detalle?}

In a first step, the time series of EUV images is used to solve a SRT problem, for each EUV band independently. As a result, the 3D distribution of the so called {filter band emissivity} (FBE) is determined for each band separately. The FBE, {an emissivity-type quantity}, is defined as the wavelength integral of the coronal EUV spectral emissivity and the telescope's passband function of each EUV channel. Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series. To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all pairs of synthetic and real images is minimized. Spatial regularization terms are also included in the objective function as to minimize high frequency spurious artifacts that are due to the specific characteristics of the SRT sparse projection matrix \citep{frazin_2009,frazin_2000}. {Due to optical depth issues that may affect LOSs} passing very close to the limb, and to the decay of intensity with radii, the 3D maps produced by DEMT analysis typically cover the height range 1.02 to 1.23 \rsun \ \citep{frazin_2009}.

{In a second step, the FBE values obtained for all bands in each voxel are used to constrain the determination of a {local differential emission measure} (LDEM) distribution, which describes the temperature distribution of the electron plasma contained in each individual tomographic grid voxel. Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}

@@

{
Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}. These non-reconstructed voxels are indicated as black voxels in the Carrington maps of the reconstructed DEMT reults in Section \ref{resu}.
}

@@

{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, i.e.
$E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transversal area of the magnetic flux tube at position $s$. Under a quiescent solar corona plasma regime, the conductive flux is assumed to be dominated by the electron thermal conduction, described by the usual Spitzer model \citep{spitzer_1962}
\begin{equation}\label{Fc}
F_c(s)=-\kappa_0\,{T(s)}^{5/2}\,\frac{dT}{ds}(s),
\end{equation}
where $\kappa_0 = 9.2 \times 10^{-7}  {\rm erg\,sec^{-1}\,K^{-7/2}}$ is the Spitzer thermal conductivity.}

@@

{The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube. Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + \phi_c.
\end{equation}
\noindent
where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\

\begin{equation}\label{phi_r}
\phi_r = \left( \frac{B_0 \ B_L}{B_0 + B_L} \right) \int_{0}^{L} ds \ \frac{E_r(s)}{B(s)}
\end{equation}

\begin{equation}\label{phi_c}
\phi_c = \left( \frac{B_0 \ F_{c,L} - B_L \ F_{c,0}}{B_0 + B_L} \right) 
\end{equation}

{Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations (\ref{Fc})-(\ref{Er}). Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line required to mantain a stable coronal structure.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{{\emph{Top panels:} latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey) and closed (black) traced field lines for which there are along at least five DEMT data points, for both CR2082 (left) and CR2208 (right). \emph{Bottom panels}: latitude-longitude location (at the same height) of each traced leg that meets the criteria listed in Section \ref{trace}. Type 0, I, II and III legs (see text) are shown in blue, red, violet and green, respectively, for CR-2082 (left) and CR-2208 (right).}}
\label{rpoint_demt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{{Statistical distribution of DEMT results traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$. Results for target rotations CR2082 and CR2208 are shown in blue and red color, respectively. In each panel the median value $m$ is indicated.} \notebyalbert{ (by Albert) The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading. Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.} }
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
\caption{{Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right). From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.} \notebyalbert{(by Albert) En el XYOUTS podés poner la letra griega $\phi$ usando los comandos ``!4" y ``!3",  y para que te salga r,c,h como subíndice pero no tan pequeño usá: ``!Dp!N", dónde p=r,c,h.}}
\label{energia_demt}
\end{center}
\end{figure}

{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities $\phi_h$, $\phi_r$ and $\phi_c$ in green, blue and red color, respectively.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).} \notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height. I believe it is interesting to compare these two curves with Figure 10. Note that while in this Figure all latitudes are magnetically open, in Figure 10 only the part at latitudes larger than the vertical black lines are open. Note that DEMT shows that in the open low corona $N_e$ decreases from the O/C boundary towards the poles, anti-correlating with the AWSoM terminal speed, which is nice. In order to quantify this anti-correlation we need to trace the terminal speed and the DEMT $N_e$, which we may need to do with the help of Chip and Nishtha. Chip, we can discuss this idea over Skype after Xmas if you are around.}}
\label{perf_lon_vr}
\end{center}
\end{figure}

@@

%\diego{We could say something about the anti correlation between speed and density and not get into the trace because issues do always appear and we don't have much time, and we all want to be happy in january. Unless the collaborators find easy to make this part.}
